%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Manager QA Operations Drug Product} % Job title
    {Moderna} % Organization
    {Madrid, Spain} % Location
    {Nov 20 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Primary QA contact and PIP presence at the fill-finish contract manufacturing organization (CMO).}
            \item {QA oversight of CMOs and testing facilities to ensure compliance with internal policies and procedures, specifications and regulatory requirements.}
            \item {Review and approve all cGMP documentation, including policies/SOPs, validation protocols/reports, equipment and process validation lifecycle documentation, batch records, deviations and CAPAs.}
            \item {Review and coordinate all changes made to the manufacturing, testing, and control processes, including those initiated by the CMO.}
            \item {Collaborate with MS\&T, QC, QA Systems and Compliance, QA Disposition, Supply Chain to support ongoing operational activities, resolve issues and continuous improvement.}
            \item {Quality counterpart for the implementation of new projects at the CMO. Oversight and approval of the validation activities, supporting submission activities.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Quality and Regulatory Manager} % Job title
    {Carl Zeiss Meditec} % Organization
    {Madrid, Spain} % Location
    {Feb 18 - Nov 20} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Head of the QA and Regulatory Department. Responsible for managing a small team in charge of the Quality, Regulatory and Environment departments.}
            \item {SPOC for Quality, Regulatory and Environment topics with the Authorities and the manufacturer (HQ).}
            \item {Responsible for implementing and maintaining Quality System Certifications (ISO9001:2015, ISO17025:2017) and the Environmental System Certification (ISO14001:2015).}
            \item {Analysis and monitoring KPIs. Lead for Management Review meeting.}
            \item {Local Management System Officer. Ensure compliance of the local affiliate QMS to the Global Standards.}
            \item {Registration of Medical Devices in Health Authorities.}
            \item {Market surveillance of Medical Devices.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Supplier Quality Manager, Medical Devices} % Job title
    {Hoffmann-La Roche} % Organization
    {Basel, Switzerland} % Location
    {Jun 16 - Dec 17} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Quality oversight of Medical Device CMOs as per the applicable regulations, guidelines, GMP and Roche Standards.}
            \item {Evaluate and solve a wide range of complex issues that affect multiple functions/sites related to direct material discrepancies, market complaints and associated investigations.}
            \item {Initiate, assess, and manage vendor-initiated change, and third-party actions for Roche initiated change per applicable regulations, guidelines, and Roche standards.}
            \item {Supplier Audit.}
            \item {Continuous monitoring and trending of the qualified Suppliers. Identify, define and implement supplier corrective and improvement projects.}
            \item {Create and Negotiate Quality Agreements. Provide quality requirements and negotiate final Supply specifications.}
            \item {Participate in due diligence assessment for Supplier selection, Lead Supplier qualification and maintain its approved state through consistently satisfactory performance.}
            \item {Strive to meet company and department goals and metrics.}
            \item {Elaboration and revision of Device Design documentation, such as Validation Master Plan, Design History File, OQ/IQ/PQ.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Quality Assurance (QA) Operations Specialist} % Job title
    {Roche} % Organization
    {Madrid, Spain} % Location
    {Jun 15 - May 16} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Hands-on performing in-process Quality Assurance checks for tablets and capsules.}
            \item {Lead deviations and investigations occurred during the production processes, propose corrective and preventive actions (CAPA) to solve problems, reduce recurrences, and monitor effectiveness.}
            \item {Develop technical documentation to evaluate product performance, analyze trends, and propose actions, such as Annual Product Quality Reviews (APQR) and Periodic Quality Evaluations (PQE).}
            \item {Writing and review of local procedures, Quality Agreements, Global Standards and Specifications.}
            \item {Ensure product quality and reliability inside all departments related to product manufacturing.}
            \item {Batch record review.}
            \item {Complaint management. Investigation and reporting product customer complaints.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Quality Assurance (QA) Specialist Utilities and Engineering} % Job title
    {Eli Lilly} % Organization
    {Florence, Italy} % Location
    {Sep 13 - Mar 15} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {QA of the Clean Utilities used for the production of biotech FP.}
            \item {Change control, assessing and investigating deviations, CAPAs, complaints and periodic quality evaluations.}
            \item {Monthly monitoring and trending reporting for the Clean Utilities.}
            \item {Established new objectives and introduced a quality culture inside the engineering projects, maintenance and facility management.}
            \item {QA representative for facility management, pest control and engineering projects.}
            \item {SME during external and internal audits.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Health and Safety Specialist} % Job title
    {Eli Lilly} % Organization
    {Florence, Italy} % Location
    {Feb 13 - Aug 13} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Catastrophic Risk Assessment.}
            \item {Site Business Continuity Plan.}
            \item {Site Pandemic Plan.}
            \item {Chemical Safety.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Health and Safety Coordinator in Construction Sites} % Job title
    {Coordinación de Seguridad y Proyectos} % Organization
    {Madrid, Spain} % Location
    {Mar 10 - Dec 12} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Management of occupational safety risks on a range of industrial, retail and residential construction sites.}
            \item {Identification of hazards and injury reduction through direct dealing with contractors and subcontractors, mediating with the project management.}
            \item {Making technical decisions based on applying the safety principles established by law.}
        \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%% cSpell: ignore Coordinación Seguridad Proyectos